### 2012-11-19 intention motor representation joint action (paper 3)/conf budapest philosophy 2012-11/shared agency and motor representation GOAL VERSION v2.tex
ceu talk in preparation

\section{***Discussion with Cordula Vesper}
\begin{enumerate}
\item Say more about what shared agency at the start: use the contrast cases instead of examples, and say that it involves some kind of fusing of agency.
\item Note that in the jumping experiments, only the subject with the shorter jump changes what she does depending on the difference in jump-length between the two subjects.  Vesper et al interpret this as showing that the subject with the shorter jump plans the whole activity.  But it isn't obviously reciprocal: there is no evidence that the subject with the longer jump is similarly planning.  And this makes sense: here they achieve coordination by first distributing roles (a strategy) and then having at least one subject plan both actions (so there is slightly less reliance on the two plans coinciding).  
Of course the appearance that they are distributing roles might just be an artefact of reciprocal planning where the upshot of the planning is that the person with the longer jump just does what she would normally do.

\item {[done]}  Don't say `neither shared nor an intention' unless you explain this.
\item {[done]} Can cite \citet{konvalinka:2010_follow} as example of what happens when two people each try to predict the other.
\end{enumerate}

\section{***Discussion with Hong Yu}
`Once we move beyond the single agent there's no a priori reason to suppose that you have a single kind of agentive structure' (Hong Yu).
This is slightly tricky for me because I don't think there's a single kind of agentive structure in individual action either.

Dissimilarity between this paper and the paper on intention and motor representation: whereas it was maybe plausible to conjecture that all intentions bottom out in motor representation, it is not similarly plausible to claim that shared intentions bottom out in social motor representations (there are surely cases of shared agency where the sharing is entirely a matter of intention and does not involve motor representations at all).

Hong Yu suggested that we need to include the argument about format in order to argue that motor representations have a role distinct from that of shared intention.

In discussion: I need to shift this paper from saying:
\begin{quote}
There is a form of shared agency and that form cannot be characterised without reference to motor representation.
\end{quote}
to saying:
\begin{quote}
There are at least two forms of shared agency (at least two agentive structures) and some of these are such that characterising them involves appeal to motor representation.
\end{quote}
This shift reveals a new problem: we become more open to the objection that philosophy should concern forms of shared agency involving intention only.

I need to stress the \emph{parity argument}.
The argument is this:
If 
\begin{quote}

	two or more agents' actions being appropriately related to a shared intention (as Bratman characterises it) is sufficient for shared agency, 
\end{quote}
then
\begin{quote}
	two or more agents' actions being appropriately related to a structure of social motor representation is also sufficient for shared 
	agency.
\end{quote}

\section{Introduction}
When members of a flash mob in the Central Cafe respond to a pre-arranged cue by noisily opening their newspapers, they exercise shared agency. 
But when someone not part of the mob just happens to noisily open her newspaper in response to the same cue, her action does not involve shared agency.%
\footnote{
See \citet{Searle:1990em}; in his example park visitors simultaneously run to a shelter, in once case as part of dancing together and in another case because of a storm. 
Compare \citet{Pears:1971fk} who uses contrast cases to argue that whether something is an ordinary, individual action depends on its antecedents. 
}
To give another example, 
 two former members of the mob exercise shared agency when they 
   later walk to the metro station together. 
But two people who merely happened to be walking to the metro station side by side would not be exercising shared agency \citep{gilbert_walking_1990}. 
These sorts of case invite the question, 
How do actions involving shared agency differ from merely parallel actions involving  only individual agency?

The first example shows that the difference between shared agency and parallel individual agency can’t just be that the resulting actions have a common effect because merely parallel actions can have common effects too. 
And the second example shows that the difference can’t just be a matter of coordination, because people who are merely happen to be walking side by side each other also need to coordinate their actions in order to avoid colliding.  
Apparently, then, systematically distinguishing cases of shared agency from cases of parallel but merely individual agency  requires reflection on causes of actions.

%
%Shared agency is paradigmatically involved when two (or more) people 
%	paint a house together \citep{Bratman:1992mi}, 
%	lift a heavy sofa together \citep{Velleman:1997oo}, 
%	prepare a hollandaise sauce together \citep{Searle:1990em}, 
%	go to Chicago together \citep{Kutz:2000si}, 
%	and walk together \citep{gilbert_walking_1990}.
%In developmental psychology paradigm cases involving shared agency include  two people 
%	tidying up the toys together \citep{Behne:2005qh},
%	cooperatively pulling handles in sequence to make a dog-puppet sing \citep{Brownell:2006gu},
%	bouncing a ball on a large trampoline together \citep{Tomasello:2007gl}.

Which representations %and processes 
are needed to distinguish shared from individual agency?
Philosophers have so far considered intentions and commitments but ignored the possibility that appeal to motor representations may also be needed. 
%To considerations jointly motivate considering whether fully characterising shared agency may require appeal to motor representation.
By contrast, concerning individual rather than shared agency, some have argued that motor representation may play a role in explaining agency \citep[e.g.][]{pacherie:2000_content,pacherie:2008_action,butterfill:2012_intention}. 
In addition, scientific research provides evidence that motor representations sometimes play a role in enabling agents to exercise shared agency, as we shall explain in detail below.
So it is possible to ask whether appeal to motor representation  %might not only sometimes enable agents to exercise shared agency but also
could also play a role in distinguishing shared from individual agency.
In this paper we argue that it could.
Shared agency is not always only a matter of our intentions or commitments: in some cases it also constitutively involves certain structures of motor representation.
Or so we aim to show.

Before going further,
let us step back to ask 
	why it might be useful 
	to  distinguish systematically between shared and individual agency?
Shared agency raises a tangle of scientific and philosophical questions.  Psychologically we want to know which mechanisms make it possible \citep{Sebanz:2006yq,vesper_minimal_2010}.  
Developmentally we want to know when shared agency emerges, what it presupposes and whether it might somehow facilitate socio-cognitive, pragmatic or symbolic development \citep{Moll:2007gu,Hughes:2004zj,Brownell:2006gu}.  
Phenomenologically we want to characterise what (if anything) is special about experiences of action and agency when shared agency is involved \citep{Pacherie:2010fk}.  
Metaphysically we want to know what kinds of entities and structures are implied by the existence of shared agency \citep{Gilbert:1992rs,Searle:1994lb}.  
And normatively we want to know what kinds of commitments (if any) are entailed by shared agency and how these commitments arise \citep{Roth:2004ki}.
%, plus a formal account of how practical reasoning for joint action differs (if at all) from individual practical reasoning \citep{Sugden:2000mw,Gold:2007zd}
A philosophical account of shared agency 
that made it possible to systematically distinguish shared from individual agency  
may support investigation of these questions (as \citealp{Bratman:2009lv} suggests).  
%Or, if there is more than one form of shared agency, the account should provide a principled way of distinguishing among forms of individual and shared agency.

As already mentioned, our aim is to show that distinguishing individual from shared agency sometimes involves appeal to certain structures of motor representation.
Our first step is to review standard approaches to shared agency.

\section{Shared intention}
On the leading, best developed accounts of shared agency in philosophy and psychology, 
shared agency is explained  in terms of a special kind of intention or structure of intention, knowledge and commitment often called a shared intention.
For two or more agents to exercise shared agency is for them to have a shared intention and for this shared intention to be appropriately related to their actions.
Such actions comprise a \emph{shared intentional activity} (\citealp[p.\ 142]{Bratman:1999fr}).%
%On this widely held view, the difference between our walking together and two strangers merely walking side-by-side is that one event is appropriately related to a shared intention whereas the other is not.

Explaining shared agency in terms of shared intention pushes us back to the question, What is shared intention?
Here is much disagreement.
Some hold that it differs from
ordinary intention with respect to the attitude involved (\citealp{Searle:1990em}). 
Others have explored the notion that it differs from ordinary intention with respect to its subject, which is plural \citep{Gilbert:1992rs,helm_plural_2008}, 
or that it differs from ordinary intention in the way it arises, namely through team reasoning \citep{Gold:2007zd}, 
or that it involves distinctive obligations or commitments to others (\citealp{Gilbert:1992rs}; \citealp{Roth:2004ki}).
Opposing all such views, \citet{Bratman:1992mi,Bratman:2009lv} argues that shared intention can be realised by multiple ordinary individual intentions and other attitudes whose contents interlock in a distinctive way.

To avoid having to take sides on what shared intention is, 
let us abstract the details
and focus on features that everyone should agree on.
Minimally, a shared intention stands to the actions comprising a shared intentional activity in roughly the way that an ordinary, individual intention stands to an ordinary, individual action.
Now an ordinary, individual intention represents an outcome, coordinates an agent's actions, and coordinates the agent's actions in such a way that, normally, this coordination would facilitate the occurrence of the represented outcome.
Similarly, 
on almost any account,
a shared intention involves there being a single outcome which each agent represents, where these representations coordinate the several agents' actions and coordinate them in such a way that, normally, the coordination would facilitate the occurrence of the represented outcome.

There is another feature of shared intention that should be uncontroversial.  
Shared intentions or their components feature in practical reasoning alongside ordinary, individual intentions,
 and there are normative requirements which apply to combinations of individual and shared intentions.
To illustrate, tonight there is a party and a ceremony.
It is impossible for anyone to attend both, and this is common knowledge among us.
We have a shared intention that we attend the ceremony together.
While having this shared intention, I also intend to go to the party. 
Give our common knowledge,
this combination of shared and individual intentions is irrational. 
Its irrationality is related to that which would be involved in my individually intending to attend the ceremony while also intending to go to the party.
In short, shared intentions or their components are inferentially and normatively integrated with ordinary, individual intentions.

So much for shared intention.
Can we give a full account of shared agency by saying (roughly) that exercises of shared agency involve agents acting on a shared intention?
Or are further ingredients necessary in systematically distinguishing shared from individual  agency?
Our view is that further ingredients are necessary.
In giving a full account of shared agency, it is also necessary to appeal to certain structures of motor representation. 
Note, however, that our view is consistent with various weaker claims linking shared intention to shared agency.
Our view is consistent with the claim that appeal shared intention is also needed in giving an account of shared agency,  
%and with the claim that \emph{some forms} of shared agency can be fully characterised by appeal to shared intention alone.
and with the claim that all exercises of shared agency involve shared intentions in some way.%
\footnote{
On the latter claim, see \citet[p.\ 5]{Gilbert:2006wr}: `I take a collective action to involve a collective intention.'  
Related claims are made by 
	\citet[p.\ 381]{Carpenter:2009wq}, 
	\citet[p.\ 369]{Call:2009fk}, 
	\citet{Kutz:2000si},  
	\citet[p.\ 117]{rakoczy_pretend_2006},  and
	\citet{Tollefsen:2005vh}.
}

\section{An objection}
At this point opponents sometimes attempt to dismiss our view out of hand along these lines.
Philosophers are interested in shared \emph{intentional} agency. 
If there are forms of shared agency other than this one, we might be right to claim that understanding these will require appeal to motor representation.
But---so the objection---such forms of shared agency (if they exist at all) are not of interest to philosophers. 
So we are clearly wrong to claim that the philosophical project of distinguishing shared from individual agency might require appeal to ingredients other than shared intentions.

One possible response to this line of opposition would be to weaken our claim. 
We could become neutral on whether a full account of the sort of shared agency philosophers have focussed on can be given without appeal to motor representation,
but insist that there is a form of shared agency about which parallel philosophical questions arise. 
This conciliatory response would preserve most of the key claims in what follows, but a stronger response is available.

As mentioned above, some have argued that fully characterising individual agency requires appeal to motor representation as well as intention \citep{pacherie:2000_content,butterfill:2012_intention}. 
These arguments concern intentional action.
So if (as we suppose) these arguments are not known to be defective,
then, assuming a parallel between individual and shared agency,  
it should not be assumed at the outset that appealing to motor representation in a philosophical account of shared agency implies that the account does not apply to what opponents call `shared intentional agency'.
We do not state our position in exactly the terms used by our opponent because of doubts about the qualifier `intentional' that are not specific to discussions of shared agency.\footnotemark \  \ 
However, we do aim show in what follows that a philosophical account of the sort of shared agency that philosophers have been interested in will require appeal to structures of motor representation.

\footnotetext{ 
We avoid using the qualifier `intentional' for reasons not specific to questions about shared agency. 
(We do use the term `shared intentional activity', but our use merely follows Bratman's stipulation that this term applies to an activity appropriately related to a shared intention.)
Briefly, some philosophers offer reasons for holding that there could be agents whose actions are intentional although  the agents have no intentions at all.
For instance, Bratman describes a creature who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally' (\citeyear[p.\ 251]{bratman:2000_valuing}; see \citealp[pp.\ 137--8]{Bratman:1987xw} for further justification). 
These and related considerations reveal a coherent and natural way of using the term `intentional' on which it would apply to actions in virtue of their being appropriately related to motor representations of outcomes to which they are directed. 
It is not obvious to us whether using the term in this way is incorrect.
}

\section{Shared motor representation}
Our argument starts with an empirical premise about enabling conditions for shared agency: there are reciprocal, agent-neutral motor representations of outcomes whose obtaining would normally involve action on the part of each agent;
moreover, these structures of motor representation sometimes facilitate coordination when agents exercise shared agency.
This needs unpacking. 
So before considering evidence for this premise (in the next section), let us first explain  it.

@@

>>>>

%
%
%\section{***Discussion with Cordula Vesper}
%\begin{enumerate}
%\item Say more about what shared agency at the start: use the contrast cases instead of examples, and say that it involves some kind of fusing of agency.
%\item Note that in the jumping experiments, only the subject with the shorter jump changes what she does depending on the difference in jump-length between the two subjects.  Vesper et al interpret this as showing that the subject with the shorter jump plans the whole activity.  But it isn't obviously reciprocal: there is no evidence that the subject with the longer jump is similarly planning.  And this makes sense: here they achieve coordination by first distributing roles (a strategy) and then having at least one subject plan both actions (so there is slightly less reliance on the two plans coinciding).  
%Of course the appearance that they are distributing roles might just be an artefact of reciprocal planning where the upshot of the planning is that the person with the longer jump just does what she would normally do.
%
%\item {[done]}  Don't say `neither shared nor an intention' unless you explain this.
%\item {[done]} Can cite \citet{konvalinka:2010_follow} as example of what happens when two people each try to predict the other.
%\end{enumerate}
%
%
%
%\section{***Discussion with Hong Yu}
%`Once we move beyond the single agent there's no a priori reason to suppose that you have a single kind of agentive structure' (Hong Yu).
%This is slightly tricky for me because I don't think there's a single kind of agentive structure in individual action either.
%
%Dissimilarity between this paper and the paper on intention and motor representation: whereas it was maybe plausible to conjecture that all intentions bottom out in motor representation, it is not similarly plausible to claim that shared intentions bottom out in social motor representations (there are surely cases of shared agency where the sharing is entirely a matter of intention and does not involve motor representations at all).
%
%Hong Yu suggested that we need to include the argument about format in order to argue that motor representations have a role distinct from that of shared intention.
%
%In discussion: I need to shift this paper from saying:
%\begin{quote}
%There is a form of shared agency and that form cannot be characterised without reference to motor representation.
%\end{quote}
%to saying:
%\begin{quote}
%There are at least two forms of shared agency (at least two agentive structures) and some of these are such that characterising them involves appeal to motor representation.
%\end{quote}
%This shift reveals a new problem: we become more open to the objection that philosophy should concern forms of shared agency involving intention only.
%
%I need to stress the \emph{parity argument}.
%The argument is this:
%If 
%\begin{quote}
%
%	two or more agents' actions being appropriately related to a shared intention (as Bratman characterises it) is sufficient for shared agency, 
%\end{quote}
%then
%\begin{quote}
%	two or more agents' actions being appropriately related to a structure of social motor representation is also sufficient for shared 
%	agency.
%\end{quote}

\section{Introduction}
Shared agency is a familiar feature of everyday life, but it's hard to get a good fix on it without assuming a big chunk of theory.
I think the best available way to zoom in on shared agency is to think about contrast cases, that is pairs of cases which are as similar as possible except one involves shared agency and the other involves parallel but merely individual agency.

When members of a flash mob in the Central Cafe respond to a pre-arranged cue by noisily opening their newspapers, they exercise shared agency. 
But when someone not part of the mob just happens to noisily open her newspaper in response to the same cue, her action does not involve shared agency.%
\footnote{
See \citet{Searle:1990em}; in his example park visitors simultaneously run to a shelter, in once case as part of dancing together and in another case because of a storm. 
Compare \citet{Pears:1971fk} who uses contrast cases to argue that whether something is an ordinary, individual action depends on its antecedents. 
}
To give another example, 
 two former members of the mob exercise shared agency when they 
   later walk to the metro station together. 
But two people who merely happened to be walking to the metro station side by side would not be exercising shared agency \citep{gilbert_walking_1990}.

I'll use the term \emph{joint action} for an exercise of shared agency, as contrasted with an \emph{individual action} which is an exercise of individual agency.

A basic question about joint action is,
What is the relation between a joint action and the outcome or outcomes to which it is directed?
Ayesha and Beatrice lift the table. ***

The standard answer to this question involves shared intention.
It's hard to say exactly what a shared intention is because each philosopher seems to take a different view.
But for my purposes it's enough to say that shared intention, whatever exactly it is, stands to joint action as ordinary, individual intention stands to ordinary, individual action.
Building on this parallel,
we can say that when two or more agents act on a shared intention that they free they cat,
\begin{enumerate}
\item the shard intention involves a representation on the part of each agent of this outcome, the freeing of the cat
\item the shared intention coordinates the several agents' actions
\item and the shared intention coordinates their actions in such a way that, normally, the coordination would facilitate the occurrence of the represented outcome. 
\end{enumerate}
In this way we can explain the directedness of a joint action to an outcome by appeal to shared intention.

There is another feature of shared intention that should be uncontroversial on any account of it.  
Shared intentions or their components feature in practical reasoning alongside ordinary, individual intentions,
 and there are normative requirements which apply to combinations of individual and shared intentions.
To illustrate, tonight there is a party and a ceremony.
It is impossible for anyone to attend both, and this is common knowledge among us.
We have a shared intention that we attend the ceremony together.
While having this shared intention, I also intend to go to the party. 
Give our common knowledge,
this combination of shared and individual intentions is irrational. 
Its irrationality is related to that which would be involved in my individually intending to attend the ceremony while also intending to go to the party.
In short, shared intentions or their components are inferentially and normatively integrated with ordinary, individual intentions.

In this talk I'm going to argue that in some cases of joint action,
the directedness of the joint action to an outcome cannot be explained in terms of shared intention.
In some cases, the directedness of a joint action to a goal needs to be explained in terms of a special structure of motor representation.
I'll call this \emph{shared motor representation}.
As we'll see,
shared motor representation \textbf{resembles} shared intention in that if our actions are controlled by a shared motor representation, then:
%
\begin{enumerate}
\item there is a single outcome which we each represent 
\item and these representations coordinate our actions
\item and coordinate them in such a way that, normally,  the coordination would facilitate the occurrence of the represented outcome. 
\end{enumerate}
%
But shared motor representation \textbf{differs} from shared intention in not integrating in practical reasoning with ordinary individual intention.
There are normative constraints linking ordinary intentions to shared intentions,
but no  normative constraints link intention to shared motor representation.

I should say, right at the start, that this speculative philosophy.
The view inspired by some findings which provide some support for it, but the findings don't establish that the view is correct.

This then is my thesis.
To understand shared agency we need to understand the relation between joint actions and the  outcomes to which they are directed.
And understanding this relation requires appeal, not only to structures of intention, commitment and knowledge, 
but also to structures of motor representation.
Shared agency is not always only a matter of our intentions or commitments: in some cases it also constitutively involves certain structures of motor representation.
Or so I aim to show.

This conflicts with the view that understanding shared agency requires understanding only shared intention.
So I disagree with Facundo Alonso's statement that:
%
\begin{quote}
`the key property of joint action lies in its internal component [...] in the participants' having a ``collective'' or ``shared'' intention' \citep[pp.\ 444-5]{alonso_shared_2009}.
\end{quote}
%
But my disagreement is not terribly radical.
I'm not denying that appeal shared intention is also needed in giving an account of shared agency,  
%and with the claim that \emph{some forms} of shared agency can be fully characterised by appeal to shared intention alone.
and I'm not even disagreeing here with those who claim that all exercises of shared agency involve shared intentions in some way.
The point is just that we can't fully understand shared agency in terms of intention, commitment and knowledge:
instead, it's also necessary to invoke motor representations.

Before I start on this,
why should anyone care?
Shared agency raises a tangle of scientific and philosophical questions.  
%
\begin{enumerate}
\item Psychologically we want to know which mechanisms make it possible \citep{Sebanz:2006yq,vesper_minimal_2010}.  
\item Developmentally we want to know when shared agency emerges, what it presupposes and whether it might somehow facilitate socio-cognitive, pragmatic or symbolic development \citep{Moll:2007gu,Hughes:2004zj,Brownell:2006gu}.  
\item Phenomenologically we want to characterise what (if anything) is special about experiences of action and agency when shared agency is involved \citep{Pacherie:2010fk}.  
\item Metaphysically we want to know what kinds of entities and structures are implied by the existence of shared agency \citep{Gilbert:1992rs,Searle:1994lb}.  
\item And normatively we want to know what kinds of commitments (if any) are entailed by shared agency and how these commitments arise \citep{Roth:2004ki}.
%, plus a formal account of how practical reasoning for joint action differs (if at all) from individual practical reasoning \citep{Sugden:2000mw,Gold:2007zd}
\end{enumerate}
%
Maybe identifying a constitutive role for motor representation in shared agency will, in a small way,
 support investigation of these questions.  
%Or, if there is more than one form of shared agency, the account should provide a principled way of distinguishing among forms of individual and shared agency.

\section{The theory (non-motor)}
I want to start by sketching the theory in a way that abstracts from motor representation,
  so that you can see the general outlines.
  This will involve introducing a series of ideas.  
We'll come to the evidence only right at the end.

\subsection{*distributive goal}
Two or more agents' actions have a distributive goal just if ...

Contrast cases: don't have distributive goal.

But some actions involving parallel but merely individual agency do involve distributive goals.  
One dark night two people each independently intend to paint a large bridge red.   
More exactly, each intends that her painting grounds or partially grounds the bridge's being painted red.\footnote{
Event $D$ \emph{partially grounds} event $E$ if there are events including $D$ which ground $E$.
(So any event which grounds $E$ thereby also partially grounds $E$; 
we nevertheless describe actions as `grounding or partially grounding' events for emphasis.)
See the definition of \emph{plural grounding} *.
}  
(These intentions ensure that it is possible for both people to succeed in painting the bridge, as well as for either of them to succeed alone.)
Because the bridge is large and they start from different ends, the two people have no idea of each other's involvement until they meet in the middle.
Nor did they expect that anyone else would be involved in painting the bridge red.  
On almost any account, this implies that they were not acting on a shared intention.
Despite this, 
they both succeed in painting the bridge red. 
As this illustration suggests, 
it is possible for two or more agents' actions to have a distributive goal without them thereby exercising shared agency.
So distributive goals are not shared intentions.

\subsection{*collective goal}
Let an outcome, possible or actual, be a \emph{collective goal \label{df_collective_goal}} of a joint action, or of any collection of goal-directed actions, where three conditions are met: 
	(a) this outcome is a distributive goal of the actions; 
	(b) the actions are coordinated; and 
	(c)  coordination of this type would normally  facilitate occurrences of outcomes of this type.  
Examples of actions  that typically have collective goals include two people jointly sawing a log with a two-handled saw and  
three people jointly lifting a heavy table.
The bridge painters (from section *) are different: their actions do not have a collective goal because they are not coordinated.

Where two or more agents' actions have a collective goal there is a sense in which, taken together, their actions are directed to the collective goal.  
It is not just that each agent individually pursues the collective goal; in addition, there is coordination among their actions which plays a role in bringing about the collective goal.  
We can put this in terms of the direction metaphor.  
Any structure or mechanism providing this coordination is directing the agents' actions to the collective goal.  
So the notion of a collective goal provides a schematic answer to the question about the relation between joint actions and the goals to which they are directed.

The notion of a collective goal assumes that of coordination.  This should be understood in a broad sense.  
When two agents between them lift a heavy block by means of each agent pulling on either end of a rope connected to the block via a system of pulleys, their pullings count as coordinated in this broad sense.  
In this case, the agents' actions are coordinated by a mechanism in their environment, the rope, and not necessarily by any psychological mechanism.  
By invoking a broad notion of coordination 
and invoking coordination of actions rather than of agents,
the definition of collective goal avoids direct appeal to psychological states.

%as well as non-psychological factors such as the dynamical properties of agents' bodies \citep[e.g.][]{schmidt_richardons:_2008}.
To make a conjecture based on work with bees and ants, in some cases
the coordination needed for a collective goal may even be supplied by 
	 behavioural patterns \citep{seeley2010honeybee}  
	 and 
	 pheromonal signals \citep[pp.\ 178-83, 206-21]{hoelldobler2009superorganism}.

This is not to say that collective goals never involve psychological states.
%The notion of a collective goal is more abstract than shared intention and other notions that have been used in characterising joint action.
%On many or all accounts, shared intentions function in part to coordinate actions in such a way as to facilitate realisation of the shared intention.
In fact,
one way for several actions to have a collective goal is for their agents to be acting on a shared intention; 
a shared intention supplies the required coordination.

But the possibility we are interested in is that the coordination required for a collective goal involves structures of motor representation rather than shared intention.
How could this work in principle?

*Aim: Describe reciprocal agent-neutral planning for outcomes whose obtaining would normally involve action on the part of each agent.

\subsection{Agent-neutral}

First we need to introduce the notion of an agent-neutral plan.
By saying that something is \emph{agent-neutral} I mean just that it does not involve identifying any particular agents.

%Having an agent-neutral plan makes perfect sense if you're stranded on a desert island because, after all, there it's obvious that you're going to do everything so there's no need to specify who will bring in the washing.

Agent-neutral planning for outcomes whose realisation would normally involve action on the part of several agents is also quite common.
For example, some housemates who have decided to take on an allotment to grow vegetables might sit down together to plan what needs doing without yet assigning roles to particular individuals. 
In so planning, each housemate is thinking about what is to be done and not what she herself will do.  
%(This is an idealisation, of course.)
At some point the housemates stop planning.
(This does not necessarily mean that they have a fully worked out plan; like any other plans, agent-neutral plans can have gaps that may need filling in later.)
They now divide up the roles in a way that everyone is prepared to go along with,
	and that each implements her part in the plan.

In the above example of agent-neutral planning,
	the housemates \textbf{plan together} and \textbf{agree} on a common plan.
But an individual can construct an agent-neutral plan by herself, even if its eventual execution will involve others.
	In fact, two or more individuals who are assigned a task might each individually engage in agent-neutral planning in parallel.

Of course, for us to engage in reciprocal, parallel agent-neutral planning concerning a particular outcome only makes sense if the  plans we construct will be identical or similar enough that differences don't matter.
And, of course, we must also all assign the same or similar roles to ourselves and each other.
So reciprocal, parallel agent-neutral planning only makes sense where: 
\begin{enumerate}
\item 	we have relevantly similar planning strategies and expertise
\item there is one salient way for us to achieve the outcome; and
\item there is one salient way for us to assign roles to each other.
\end{enumerate}

	The task demands and their planning strategies may conspire to ensure that they each come up with the same agent-neutral plan.
	The task demands and manifest properties of the agents, such as their distribution in space, may also ensure that each agent also assigns the same roles to the same individuals.
(Strictly speaking it is not necessary for the plans and role assignments to be identical; it is enough if the resulting agent-specifying plans are, in a special sense, compatible.%
\footnote{
\label{fn:df_compatible}
Suppose that, for some outcome, two or more agents each have a plan for the realisation of that outcome. 
(These plans may, but need not, specify roles for all of the agents; but the plans must be agent-specific, not agent-neutral.)
By saying that these plans are \emph{compatible} we mean that:
(i) 
no agent would normally be prevented from performing the role she is assigned in her own plan by other agents performing the roles they are assigned in their plans;
and
(ii)
if all facts about which agents have which roles in which plans were common knowledge to the agents,
this would not affect the rationality of their each acting on the intention that they realise the outcome by performing the role she is assigned in her own plan.
%	each agent could rationally act on the intention that they realise the outcome by performing the role she is assigned in her own plan,
%	and she could do so even if all facts about which agents are performing which roles in which plans were common knowledge to the agents.
To illustrate, suppose that our task is to press a button simultaneously. 
If your plan is that each of us will to start to move in exactly 60 seconds and press the button 5 seconds later whereas my plan specifies that you are the leader and we are each to press the button 5 seconds after you start moving, then our plans are compatible.
})
%
Finally, each agent may know enough about herself and the others to be able to determine, without communicating, whether the plan and role assignments will be acceptable to everyone. 
	And all of this---that they engage in parallel, agent-neutral planning resulting in identical (or compatible) plans and role assignments, which are acceptable to all---may be common knowledge to the agents.
	So it is possible, in principle at least, 
	that several agents might each individually engage in agent-neutral planning and rationally perform their part in the resulting plan, knowing that the others will do likewise.
	Parallel, agent-neutral planning can rationally result in coordinated action without presupposing shared agency.%
\footnote{
Note that we are claiming only that shared agency is not presupposed.
Our view is consistent with (but does not depend on) the claim
that
	if some agents each engage in parallel, agent-neutral planning and then rationally perform their part in the resulting plan,
	the upshot would be an exercise of shared agency.
}

\subsection{*}
Having each agent plan the whole joint action means that (i) each agent plans the other agent's action,
(ii) each agent's plan for the other agent's action is approximately the same as that agent's plan for her own action [***AMBIGUOUS: `that agent's plan' must refer to the other agent, not `each agent',
and 
(iii) each  agent's plans for their own action are constrained by the plans for the other agent's action.

\textbf{So what enables the two agents' plans to mesh is not that they represent each other's plans but more simply that they plan each other's actions as well as their own actions as if they were each about to do the whole thing themselves.}

Each agent is planning (and monitoring) both their actions almost as if a single agent were going to execute the whole action.
And of course this is exactly what we want for small-scale joint action---we want two or more agents to act as one.

So what is the difference between the individual and the joint case?  From the present point of view, the primary difference may be that in joint action there is a need to prevent execution of the parts of the action which are not one’s own.

So far: shown theoretically how there could be directedness of joint action to outcome by appeal to reciprocal representations of outcomes which trigger agent-neutral planning.

But unclear that any such representations exist, or at least that they plan any significant role in ordinary cases of joint action.
What makes this theoretical possibility interesting is evidence that these representations occur in motor control of action.

***section: say what motor processes are; examine what would be evidence for different points.

\section{Shared motor representation}
Our argument starts with an empirical premise about enabling conditions for joint action: there are reciprocal, agent-neutral motor representations of outcomes whose obtaining would normally involve action on the part of each agent;
moreover, these structures of motor representation sometimes facilitate coordination when agents exercise shared agency.
This needs unpacking. 
So before considering evidence for this premise (in the next section), let us first explain  it.

@@

\textbf{*** explain motor representation in terms of passing object from one hand to the other}
